%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{sr-awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{2698ba}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Dominic}{Young}

\position{Automotive Finance Manager/Sales Consultant}
\address{Gorham, NH}

\email{\href{mailto:dominicyoung2015@gmail.com}{\nolinkurl{dominicyoung2015@gmail.com}}}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{Motivated salesman with 8+ years of sales experience in both
cellular and automotive sales with a promotion to Finance Manager. Eager
to leverage comprehensive, detail oriented experience with a proven
track record to drive sales and financial success to a leading
dealership.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {May 2024}
    {Dominic Young~~~·~~~Resume}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{experience}{%
\section{\faBriefcase~Experience}\label{experience}}

\begin{cventries}
    \cventry{Finance Manager}{Nucar}{Gorham, NH}{Sep. 2023 - Present}{\begin{cvitems}
\item Adept at analyzing customer credit profiles, negotiating financing terms, and ensuring compliance.
\item Skilled in building relationships, providing exceptional customer service, and maximizing profitability.
\item Proficient in finance software and staying updated on industry trends.
\end{cvitems}}
    \cventry{Sales Consultant}{Nucar}{Gorham, NH}{2021 - Present}{\begin{cvitems}
\item Engage with customers to understand their automotive needs and preferences.
\item Negotiate sales terms, including price, financing rates, and additional product offerings.
\item Provide exceptional customer service before, during, and after the sale to build long-term relationships and encourage referrals.
\item Proficient use of auto dealer software such as CDK, DriveCentric, Vauto, and Vision Menu.
\end{cvitems}}
    \cventry{Activities Supervisor}{Mountain View Grand Resort \& Spa}{Whitefield, NH}{2020 - 2021}{\begin{cvitems}
\item Delegating tasks to employees to efficiently run all resort activities.
\item Create, plan, and implement fun and creative activities and events.
\item Interact with guests in a fun and friendly manner to build memorable experiences for guests.
\end{cvitems}}
    \cventry{Wireless Sales Consultant}{Wireless Zone - Verizon Wireless Premium Retailer}{Littleton, NH}{2018 - 2020}{\begin{cvitems}
\item Engage with customers to understand their needs and recommend appropriate products and services.
\item Meet or exceed sales targets and key performance indicators (KPIs) on a consistent basis.
\item Build rapport with customers to foster long-term relationships and encourage repeat business.
\item Provide outstanding customer service before, during, and after the sale to enhance customer satisfaction and loyalty.
\end{cvitems}}
    \cventry{Wireless Sales Consultant}{GoWireless - Verizon Wireless Premium Retailer}{Newington, NH}{2016 - 2017}{\begin{cvitems}
\item Engage with customers to understand their needs and recommend appropriate products and services.
\item Meet or exceed sales targets and key performance indicators (KPIs) on a consistent basis.
\item Build rapport with customers to foster long-term relationships and encourage repeat business.
\item Provide outstanding customer service before, during, and after the sale to enhance customer satisfaction and loyalty.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{\faMortarBoard~Education}\label{education}}

\begin{cventries}
    \cventry{High School Diploma}{Colebrook Academy}{Colebrook, New Hampshire}{2015}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{certifications}{%
\section{\faUser~Certifications}\label{certifications}}

\begin{cventries}
    \cventry{Automotive Finance Compliance}{}{}{December 2023}{}\vspace{-4.0mm}
    \cventry{Driver's License - New Hampshire}{}{}{Active}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{skills}{%
\section{\faFileText~Skills}\label{skills}}

\footnotesize

\begin{itemize}
\tightlist
\item
  Customer Service (10+ years)
\item
  Sales (9 years)
\item
  Inventory Control (4+ years)
\item
  Microsoft Excel (3+ years)
\end{itemize}

\normalsize



\end{document}
