---
name: Dominic
surname: Young
position: "Automotive Finance Manager/Sales Consultant"
address: "Gorham, NH"
email: "dominicyoung2015@gmail.com"
researchgate: false
orcid: false
aboutme: |
  Motivated salesman with 8+ years of sales experience in both cellular and automotive sales with a promotion to  Finance Manager. Eager to leverage comprehensive, detail oriented experience with a proven track record to drive sales and financial success to a leading dealership.
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "2698ba"
output:
  srvitae::sr_awesomecv:
    keep_tex: true
  engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(srvitae)
library(tibble)
library(fontawesome)
```

<!-- Alternative education icon
\hypertarget{education}{%
\section{\faUniversity~Education}\label{education}}
-->

\hypertarget{experience}{%
\section{\faBriefcase~Experience}\label{experience}}

```{r Experience}
tribble(
  ~role, ~institution, ~location, ~dates, ~details,
  "Finance Manager", "Nucar", "Gorham, NH", "Sep. 2023 - Present", list(
    "Adept at analyzing customer credit profiles, negotiating financing terms, and ensuring compliance.",
    "Skilled in building relationships, providing exceptional customer service, and maximizing profitability.",
    "Proficient in finance software and staying updated on industry trends."
  ),
  "Sales Consultant", "Nucar", "Gorham, NH", "2021 - Present", list(
    "Engage with customers to understand their automotive needs and preferences.",
    "Negotiate sales terms, including price, financing rates, and additional product offerings.",
    "Provide exceptional customer service before, during, and after the sale to build long-term relationships and encourage referrals.",
    "Proficient use of auto dealer software such as CDK, DriveCentric, Vauto, and Vision Menu."
  ),
  "Activities Supervisor", "Mountain View Grand Resort & Spa", "Whitefield, NH", "2020 - 2021", list(
    "Delegating tasks to employees to efficiently run all resort activities.", 
    "Create, plan, and implement fun and creative activities and events.",
    "Interact with guests in a fun and friendly manner to build memorable experiences for guests."
  ),
  "Wireless Sales Consultant", "Wireless Zone - Verizon Wireless Premium Retailer", "Littleton, NH", "2018 - 2020", list(
    "Engage with customers to understand their needs and recommend appropriate products and services.",
    "Meet or exceed sales targets and key performance indicators (KPIs) on a consistent basis.",
    "Build rapport with customers to foster long-term relationships and encourage repeat business.",
    "Provide outstanding customer service before, during, and after the sale to enhance customer satisfaction and loyalty."
  ),
  "Wireless Sales Consultant", "GoWireless - Verizon Wireless Premium Retailer", "Newington, NH", "2016 - 2017", list(
    "Engage with customers to understand their needs and recommend appropriate products and services.",
    "Meet or exceed sales targets and key performance indicators (KPIs) on a consistent basis.",
    "Build rapport with customers to foster long-term relationships and encourage repeat business.",
    "Provide outstanding customer service before, during, and after the sale to enhance customer satisfaction and loyalty."
  )
) %>%
  detailed_entries(
    what = role,
    when = dates,
    with = institution,
    where = location,
    why = details
  )
```

\hypertarget{education}{%
\section{\faMortarBoard~Education}\label{education}}


```{r Education}
tribble(
  ~Degree, ~Year, ~Institution, ~Where, ~details,
  "High School Diploma", "2015", "Colebrook Academy", "Colebrook, New Hampshire", list(),
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = details
  )
```

\hypertarget{certifications}{%
\section{\faUser~Certifications}\label{certifications}}

```{r Certifications}
tribble(
  ~project, ~stage, ~description,
  "Automotive Finance Compliance", "December 2023", list(),
  "Driver's License - New Hampshire", "Active", list()
) %>%
  detailed_entries(
    what = project,
    when = stage,
    why = description
  )
```


\hypertarget{skills}{%
\section{\faFileText~Skills}\label{skills}}

\footnotesize

- Customer Service (10+ years)
- Sales (9 years)
- Inventory Control (4+ years)
- Microsoft Excel (3+ years)

\normalsize


